EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-05-18 draft.tex
Revised with several questions

In this paper, we have presented the EvoSwarm framework that implements an
event-based, cloud-native architecture suitable for hosting multi-population
optimization algorithms. The framework is based in industry-standard development
tools such as Docker and Docker Compose, making it easy to develop and deploy
multi-algorithm distributed experiments. The model is based on the asynchronous
exchange of messages between stateless functions that react to a continuous
stream of data. We compared the message-driven architecture we presented against
four other proposals for multi-population algorithms found in the literature. We
found that it is best suited for asynchronous multi-population algorithms.

We proposed a new methodology for the reproducible deployment and execution of
multiple experiments by specifying the infrastructure as part of an experiment
definition in both local or cloud environments. We presented the workflow of an
experiment's entire life-cycle viewed from the perspective of developers and
researchers. We tested the deployment on both local and Amazon's Elastic
Container Service.

@@

First, we focused on knowing how scaling is related to the number of populations
and workers in the system. This experiment concludes that there is an
interesting interplay, with the most benefit obtained with a number of
populations near-equal to the number of workers, which brings performance gains.
Also, we found that for lower dimensions, there is an advantage in using fewer
populations.

A second experiment centered on evaluating the algorithmic benefits (experiments
taking less time because they need fewer evaluations) of distributed
multi-algorithm algorithms. We compared the homogeneous and an ensemble of
multi-populations, using Genetic Algorithms (GAs) and Particle Swarm
Optimization (PSO) using the COCO benchmark framework for continuous functions.
We found that the set-up of these algorithms has a significant influence on
their results since diversity is essential for their performance. The ensemble
achieved better results and, in most cases, needed fewer evaluations.

>>>>

In this paper, we have presented the EvoSwarm framework that implements an
event-based, cloud-native architecture suitable for hosting multi-population % multi-algorithm? - JJ
optimization algorithms. % reproducible? It's in the title - JJ
The framework is based in industry-standard development
tools such as Docker and Docker Compose, making it easy for scientists and practitioners to develop and deploy
multi-algorithm distributed experiments. The model is based on the asynchronous
exchange of messages between stateless functions that react to a continuous
stream of data. We compared the message-driven architecture we presented against
four other proposals for multi-population algorithms found in the literature. % But it's not a practical comparison, but a theoretical one. Show the differences instead of compare? - JJ
We
found that it is best suited for asynchronous multi-population algorithms. % This is not really proved. You chose, you didn't find - JJ

We proposed a new methodology for the reproducible deployment and execution of
multiple experiments by specifying the infrastructure as part of an experiment
definition in both local or cloud environments. We presented the workflow of an
experiment's entire life-cycle viewed from the perspective of developers and
researchers. We tested the deployment on both local and Amazon's Elastic
Container Service. % and we proved... Remember the experimental hypothesis - JJ

@@

First, we focused on knowing how scaling is related to the number of populations
and workers in the system. This experiment concludes that there is an
interesting interplay, with the most benefit obtained with a number of
populations slightly above the number of workers, which brings performance gains. % of what kind? - JJ
Also, we found that for lower dimensions, there is an advantage in using fewer
populations.

A second experiment centered on evaluating the algorithmic benefits (experiments
taking less time because they need fewer evaluations) of distributed
multi-algorithm algorithms. We compared the homogeneous and an ensemble of
multi-populations, using Genetic Algorithms (GAs) and Particle Swarm
Optimization (PSO) using the COCO benchmark framework for continuous functions. % as a visualization device? - JJ
We found that the set-up of these algorithms has a significant influence on
their results since diversity is essential for their performance. The ensemble
achieved better results and, in most cases, needed fewer evaluations.
